---
title: "Discrete Choice Model Analysis"
---



```{r}
library(mlogit)
Mall=read.csv("Mall_choice_data.csv",header=T)
mall.long=mlogit.data(Mall, shape="long",choice="choice",alt.levels = c("1","2","3","4","0"))
```
```{r}
Mall.m1=mlogit(choice~discount+targeting+distance|income+gender,mall.long,reflevel = "0")
summary(Mall.m1)
```
Statistically Significant: B3, B4j and B52 and B53 are significant.
[Distance, choice 1&income, choice 2&income, choice 3&income, choice 4&income, choice 1&gender, choice 3 & gender]

	When the distance to the mall increases, the less likely the customer is to go to the mall (because their utility from going to the mall decreases)

	Higher the income of the customer, more likely it is for the customer to go to mall 1 (because their utility here from going to the mall is more than the utility from NOT going to a mall)

	Higher the income of the customer, more likely it is for the customer to go to mall 2 (because their utility here from going to the mall is more than the utility from NOT going to a mall)

	Higher the income of the customer, more likely it is for the customer to go to mall 3 (because their utility here from going to the mall is more than the utility from NOT going to a mall)

	 Higher the income of the customer, more likely it is for the customer to go to mall 4 (because their utility here from going to the mall is more than the utility from NOT going to a mall)

	When the customer is male, he is less likely to go to mall 1 (because their utility here from going to the mall is less than the utility from NOT going to a mall)

	When the customer is male, he is less likely to go to mall 3 (because their utility here from going to the mall is less than the utility from NOT going to a mall)

